Predicting sales of newly published books

### 2015-08-18 paper.tex
rehaciendo el estado del arte
Más preguntas y sugerencias para revisar por @pacastillo

\documentclass{llncs}
\usepackage{graphics}
\usepackage{amssymb}
\usepackage[dvips]{epsfig}
%\usepackage[spanish]{babel}
\usepackage[latin1]{inputenc}

@@

A company that intends to release a new product has a high risk due to
the complexity of the production and distribution processes. A newly
launched product is also new to the company, and sales forecasts can
only be based on the experience of similar products. 
In this scope, having accurate estimates of future sales of the new
product is extremely important \cite{ChingChin2010} so that production
runs do not exceed predicted sales. 
Indeed, several studies have demonstrated that improving sale predictions 
(a reduction of forecasting errors) results in an improvement in the 
production \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.

@@

In the field of publishing industry, it is more important printing an
adequate number of copies but not too much, as the unsold volumes will
lead to losses, whereas if the number of printed copies was not
enough, you can always print more. 
Thus, it is extremely important using predictive tools to optimize 
production and improve the publishing company profits or minimize losses \cite{Zhao2001}
by forecasting the sales a new book might achieve. 
An example is the optimization of sales \cite{Mattila2002} by
improving profit margins by selling the whole publishing roll.  
% [Pedro] "publishing roll" es como he encontrado "tirada editorial" traducido...

@@

Thus, it is very important to know the product and the variables that
might affect the sales, and how an expert manager can eventually 
take them into account \cite{Armstrong2001,SThomassey2014}. 
                                % ¿Esto también pasa en la industria de la
                                % moda. ¿Qué vamos a usar de esto? - JJ
                                % [Pedro] esto iba referido a la Industria Editorial.
Their impact is difficult to estimate and it is not constant over time, 
hence the difficulty to adequately identify and measure their influence \cite{DeToni2000}.
In addition, some may have correlations between them. 
However, these correlations can be detected using data analysis methods, 
such as Self-Organizing Maps (SOM) \cite{kohonen1998} 
or stepwise regression analysis (SRA) \cite{Chang2009}.

@@

% In the literature several proposals to perform the prediction of sales in different fields can be found. 
In the last years, different analysis and forecasting methods, such as
regression models \cite{Papalexopoulos1990}, neural networks \cite{Yoo1999} or fuzzy systems \cite{Mastorocostas2001} 
have been applyed in different industry sectors, i.e. electricity consumption, traffic flow or sales forecasting.

@@

Finally, in the literature different error measures can be found to report the results obtained using the prediction methods. 
Those error measurements are also called error functions or cost functions. 
%One of the most commonly used is the mean absolute error (see equation \ref{eq:MAE}).
In any case, we recommend using widely accepted standard equations\footnote{http://www.gepsoft.com/gxpt4kb/Chapter10/Section3/Introduction.htm} in order to compare obtained results with those presented in other research papers using other methods.
That is why different standard error measurements (Equations \ref{eq:MAE} to \ref{eq:RRSE}), implemented in tools like Weka\footnote{http://wiki.pentaho.com/display/DATAMINING} \cite{Witten2011} or R\footnote{https://www.otexts.org/fpp/2/5} \cite{Hyndman2013}, are proposed.

>>>>

\documentclass{llncs}
\usepackage{graphics}
\usepackage{amssymb}
\usepackage[dvips]{epsfig}
\usepackage[latin1]{inputenc}

@@

A company that intends to release a new product has a high risk due to
the complexity of the production and distribution processes. A newly
% tienes que enmarcar el problema. Se trata de productos culturales
% con soporte físico y con ventas relativamente pequeñas. Libros,
% discos, no sé si alguna cosa más. - JJ
launched product is also new to the company, and sales forecasts can
only be based on the experience of similar products. 
In this scope, having accurate estimates of future sales of the new
product is extremely important \cite{ChingChin2010} so that production
runs do not exceed predicted sales. 
Indeed, several studies have demonstrated that improving sale predictions 
(a reduction of forecasting errors) results in an improvement in the 
production \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.

@@

In the field of publishing industry, the challenge is to print an
adequate number of copies but not too much, as the unsold volumes will
lead to losses, whereas if the number of printed copies was not
enough, you can always print more. 
Thus, it is extremely important using predictive tools to optimize 
production and improve the publishing company profits or minimize losses \cite{Zhao2001}
by forecasting the sales a new book might achieve. 
An example is the optimization of sales \cite{Mattila2002} by
improving profit margins by selling the whole publishing roll.  
% [Pedro] "publishing roll" es como he encontrado "tirada editorial" traducido...

@@

Thus, it is very important to know the product and the variables that
might affect the sales, and how an expert manager can eventually 
take them into account \cite{Armstrong2001,SThomassey2014}. 
                                % ¿Esto también pasa en la industria de la
                                % moda. ¿Qué vamos a usar de esto? - JJ
                                % [Pedro] esto iba referido a la Industria Editorial.
Their impact is difficult to estimate and it is not constant over time, 
hence the difficulty to adequately identify and measure their influence \cite{DeToni2000}.
In addition, some may have correlations between them. 
However, these correlations can be detected using data analysis methods, 
such as Self-Organizing Maps (SOM) \cite{kohonen1998} 
or stepwise regression analysis (SRA) \cite{Chang2009}. % What do they
                                % do? What are the results?

@@

% In the literature several proposals to perform the prediction of sales in different fields can be found. 
In the last years, different analysis and forecasting methods, such as
regression models \cite{Papalexopoulos1990}, neural networks \cite{Yoo1999} or fuzzy systems \cite{Mastorocostas2001} 
have been applied in different industry sectors, i.e. electricity
consumption, traffic flow or sales forecasting. % ¿Y qué? Esta frase
                                % no aporta nada. La primera frase
                                % tiene que enmarcar el estado del
                                % arte - JJ

@@

Finally, in the literature different error measures can be found to report 
the results obtained using the prediction methods \cite{ChingChin2010,Madsen2008}. 
Those error measurements are also called error functions or cost functions. 
%One of the most commonly used is the mean absolute error (see equation \ref{eq:MAE}).
In any case, we recommend using widely accepted standard 
equations\footnote{http://www.gepsoft.com/gxpt4kb/Chapter10/Section3/Introduction.htm} 
in order to compare obtained results with those presented in other research 
papers using other methods.
That is why different standard error measurements (Equations \ref{eq:MAE} to \ref{eq:RRSE}), 
implemented in tools like Weka\footnote{http://wiki.pentaho.com/display/DATAMINING} \cite{Witten2011} 
or R\footnote{https://www.otexts.org/fpp/2/5} \cite{Hyndman2013}, are proposed.
